---
title: "titanic-analysis"
author: "José Luis Tello"
date: "8/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Upload packages and data!

```{r}
library(tidyverse)
library(ggthemes)
```

```{r}
train <- read.csv("data/raw/train.csv", header = TRUE)
test <- read.csv("data/raw/test.csv", header = TRUE)
```

Data classify in R it's a different from the statistics standard. 

In R we have data types and data structures. 

R data types are: 
  * character
  * numeric 
  * integer 
  * complex 
  * logical

R basic data structures include 
  * vector 
  * list
  * matrix 
  * data frame 
  * factors

Let's check the structure of our data!


```{r}
str(train)
```

```{r}
str(test)
```



Based on Understand Data section we need to make some changes. 


```{r}
train$Survived <- as.factor(train$Survived)
train$Embarked <- as.factor(train$Embarked)
train$Sex <- as.factor(train$Sex)
train$Pclass <- as.factor(train$Pclass)


test$Embarked <- as.factor(test$Embarked)
test$Sex <- as.factor(test$Sex)
test$Pclass <- as.factor(test$Pclass)
```


```{r}
str(test)
```

```{r}
str(train)
```

#Time to bind our two sets!


### Drop NA values from test set 

```{r}
test <- data.frame(test[1], Survived = rep("NA", nrow(test)), test[ , 2:ncol(test)])
```

### Merge train and test for visualization and analysis

```{r}
data <- rbind(train, test)
```

### Create file from rbind product
```{r}
write.csv(data, "./data/interim/data.cvs", row.names = FALSE )
```

```{r}
str(data)
```


### All right! now data have correct type. Time to analyze and visualize.

Let's see gender proportion by int and percent with baseR

```{r}
table(data$Sex, dnn = "Gender proportion")
prop.table(table(as.factor(data$Sex), dnn = "Gender proportion percent"))
```

Visualizing Sex Proportion with Ggplot

```{r}
ggplot(data, 
       aes(x = Sex,
           y = ..count.. / sum(..count..))) + 
  geom_bar(fill = "cornflowerblue", 
           color="black") +
  labs(x = "Gender", 
       y = "Percent", 
       title = "Proportion of gender",
       subtitle = "") +
  scale_y_continuous(labels = scales::percent) +
  theme_base()

```


# I don't like this plot... 

```{r}
ggplot(data, aes(Sex, fill = Pclass)) + 
  geom_bar(color="black") +
  labs(x = "Gender", 
       y = "Count", 
       title = "Passenger socio-economic class",
       subtitle = "Distribution per gender") +
  theme_base()
```

# This looks better

```{r}
ggplot(data, aes(x = Sex, fill = Pclass)) +
  geom_bar(color = "black", 
           position = position_dodge
           (preserve = "single")) +
  labs(x = "Gender",
       y = "Count",
       title = "Passenger socio-economic class",
       subtitle = "Distribution per gender") +
  theme_base()
```


```{r}
ggplot(data, aes(Age, fill = Sex)) +
  geom_histogram(color = "black") +
  labs(x = "Age",
       y = "Total",
       title = "Age distribution" ) +
    theme_base()
```

### At this point, we know some things. 

1. - En el titanic habían 28% más de hombres que mujeres, en numeros esto quiere decir 366 hombres. 
2. - Había mas del doble de hombres en tercera clase que mujeres, en primera y segunda estan casi iguales.
3. - La mayor distribución de edades se concentra entre los 20 y 40 años tanto para hombres como para mujeres

En este punto 















